### 2021-04-21 README.Rmd
fsfdsfs

The second piece of software is [LaTeX](https://www.latex-project.org). LaTeX is a prominent document preparation system in academia and preferred by publishers especially for its contrast to "What You See Is What You Get" word processors like Microsoft Word. `{steveproj}` ultimately places R Markdown and Pandoc---which are necessary for this package---before LaTeX in terms of document preparation. No matter, `{steveproj}` necessarily elevates LaTeX PDF documents above other output types. Interested users with no awareness of LaTeX should know `{steveproj}` imports `{rmarkdown}`, which in turn imports `{tinytex}`. This would install and maintain a version of LaTeX to compile these documents. However, the particular flavor of LaTeX template (from `{stevetemplates}`) requires one additional LaTeX dependency that `{tinytex}` does not install by default. You may encounter a vague error in rendering to PDF that reads something like this.

>>>>

The second piece of software is [LaTeX](https://www.latex-project.org). LaTeX is a prominent document preparation system in academia and preferred by publishers especially for its contrast to "What You See Is What You Get" word processors like Microsoft Word. `{steveproj}` ultimately places R Markdown and Pandoc---which are necessary for this package---before LaTeX in terms of document preparation. No matter, `{steveproj}` necessarily elevates LaTeX PDF documents above other output types.

There are two options for installing LaTeX on your system. First, you can install it yourself---in all its 4+ gigabytes of glory. For Mac users, this is "MacTeX" and you can [install it here](http://www.tug.org/mactex/). For Windows users, this is "MikTeX" and you can [install it here](https://miktex.org/). For (Ubuntu) Linux users, something like `sudo apt-get install texlive-base texlive-latex-base texlive-latex-extra` should work. Linux users are probably aware that whatever version of LaTeX comes default in their package manager of choice comes with multiple, complementary packages. Installing even `texlive-base` will probably install more of them as dependencies.

The second option is tailored for those interested users with no awareness of LaTeX. `{steveproj}` imports `{rmarkdown}`, which in turn imports `{tinytex}`. This would install and maintain a version of LaTeX to compile these documents that ostensibly precludes the need to install the more comprehensive suites available for download and installation on the internet. I will only add that users who do this should know the preferred flavor of LaTeX template (from `{stevetemplates}`) in this package requires one additional LaTeX dependency that `{tinytex}` does not install by default. You may encounter a vague error in rendering to PDF that reads something like this.
